### 2021-01-06 priority-gv.tex
Minor change.c

\subsubsection*{Internal and External Choice}
\todo{You might want to clarify (repeat) that external choice can be modeled by sum type communication only because the language uses linear channels.}
\todo{We also might want to emphasise that the modelling of choice in GV by~\cite{lindleymorris15} is unsound.}
Typically, session-typed languages feature constructs for internal and external choice. In GV, these can be defined in terms of the core language, by sending or receiving a value of a sum type~\cite{lindleymorris15}. We use the following syntactic sugar for internal ($\ty{\tyselect[\cs{o}]{S}{S'}}$) and external ($\ty{\tyoffer[\cs{o}]{S}{S'}}$) choice and their units:
\[
\begin{array}{lcl}
  \ty{\tyselect[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tysend[\cs{o}]{(\tysum{\co{S}}{\co{S'}})}{\tyends[\cs{o+1}]}} \\
  \ty{\tyoffer[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{(\tysum{S}{S'})}{\tyendr[\cs{o+1}]}} \\
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\tyselectemp[\cs{o}]}
  & \elabarrow & \ty{\tysend[\cs{o}]{\tyvoid}{\tyends[\cs{o+1}]}} \\
  \ty{\tyofferemp[\cs{o}]}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{\tyvoid}{\tyendr[\cs{o+1}]}} \\
\end{array}
\]
As the syntax for units suggests, these are the binary and nullary forms of the more common n-ary choice constructs $\ty{{\oplus}^{\cs{o}}\{l_i:S_i\}_{i\in{I}}}$ and $\ty{{\with}^{\cs{o}}\{l_i:S_i\}_{i\in{I}}}$, which one may obtain generalising the sum types to variant types. For simplicity, we present only the binary and nullary forms.

>>>>

\subsubsection*{Internal and External Choice}
\todo{You might want to clarify (repeat) that external choice can be modeled by sum type communication only because the language uses linear channels. (We also might want to emphasise that the modelling of choice in GV by~\cite{lindleymorris15} is unsound.)}
Typically, session-typed languages feature constructs for internal and external choice. In GV, these can be defined in terms of the core language, by sending or receiving a value of a sum type~\cite{lindleymorris15}. We use the following syntactic sugar for internal ($\ty{\tyselect[\cs{o}]{S}{S'}}$) and external ($\ty{\tyoffer[\cs{o}]{S}{S'}}$) choice and their units:
\[
\begin{array}{lcl}
  \ty{\tyselect[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tysend[\cs{o}]{(\tysum{\co{S}}{\co{S'}})}{\tyends[\cs{o+1}]}} \\
  \ty{\tyoffer[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{(\tysum{S}{S'})}{\tyendr[\cs{o+1}]}} \\
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\tyselectemp[\cs{o}]}
  & \elabarrow & \ty{\tysend[\cs{o}]{\tyvoid}{\tyends[\cs{o+1}]}} \\
  \ty{\tyofferemp[\cs{o}]}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{\tyvoid}{\tyendr[\cs{o+1}]}} \\
\end{array}
\]
As the syntax for units suggests, these are the binary and nullary forms of the more common n-ary choice constructs $\ty{{\oplus}^{\cs{o}}\{l_i:S_i\}_{i\in{I}}}$ and $\ty{{\with}^{\cs{o}}\{l_i:S_i\}_{i\in{I}}}$, which one may obtain generalising the sum types to variant types. For simplicity, we present only the binary and nullary forms.
